R Script V5

### 2023-05-12 Data & Scripts/MSC R Script.Rmd
March 12th
New version of the R script + PCAs. Includes pathway analyses.

> The number of crows in the area is not a good estimate of group size. The number of foraging members during the foraging event should be better.
> Whether or not the site was baited will likely affect the duration of movement, since crows will need to look for food in non-baited recordings, while the crows have easy access to a large concentration of food in baited recordings. Therefore, the baited crows are expected to move less than non-baited crows.
>I removed the observations in agricultural settings because they had no sentinels present. This could be talked about in the discussion: agricultural fields may lack perches for individuals to act as sentinels. Vineyards may have some structures, but the visibility is limited when the vines are laden with fruit.\
>I removed observations past Sept 29 because I was told behaviors can change wildly in the winter. The number of crows spotted decreased past that date, suggesting the migrants have left or were leaving. To not have to include time of year (I already have part of the breeding season), I decided to simplify.\

>>>>

> The number of crows in the area is not a good estimate of group size. The number of foraging members during the foraging event should be better.
> Whether or not the site was baited will likely affect the duration of movement, since crows will need to look for food in non-baited recordings, while the crows have easy access to a large concentration of food in baited recordings. Therefore, the baited crows are expected to move less than non-baited crows.
> #KMG: I can imagine a reviewer would want to know hwo the baiting was standardized - something to keep in mind when you are writing. I removed the observations in agricultural settings because they had no sentinels present. This could be talked about in the discussion: agricultural fields may lack perches for individuals to act as sentinels. Vineyards may have some structures, but the visibility is limited when the vines are laden with fruit.\
> #KMG: This is something that can go in the methods. You had three sites, but one was removed due to lack of sentinals, and then you can have a bit in the discussion. I removed observations past Sept 29 because I was told behaviors can change wildly in the winter. The number of crows spotted decreased past that date, suggesting the migrants have left or were leaving. To not have to include time of year (I already have part of the breeding season), I decided to simplify.\
